How to select predictive models for decision-making or causal inference?

### 2023-12-08 how_to_select_causal_models.tex
iter

The $R \text{-risk}$ targets the oracle at the cost of an overlap re-weighting
and the addition of the reweighted Bayes residuals, which are independent of
$f$. In good overlap regions the weights $e(x) \big(1-e(x) \big)$ are close to
$\frac{1}{4}$, hence the $R \text{-risk}$ is close to the desired gold-standard
$\tau \text{-risk}$. For randomized control trials, this weight is constant
making the $R\text{-risk}$ particularly suited for exploring
heterogeneity (Details in Appendix \ref{apd:theory:special_cases})

@@

We generate the response functions using random bases extension, a common method in
biostatistics, \emph{eg} functional regression with splines
\cite{howe_splines_2011, perperoglou_review_2019}. By allowing the function to
vary at specific knots, they give flexible non-linear models. The number of
knots controls the complexity of the function. We use random approximation of
Radial Basis Function (RBF) kernels \cite{rahimi_random_2008} to generate the
outcome and treatment functions. RBF use the same process as polynomial splines
but replace polynomial by Gaussian kernels. Unlike polynomials, Gaussian kernels
have decreasing influences in the input space. This avoids unrealistic
divergences of the response surfaces at the ends of the feature space. We
generate 1\,000 datasets based on these functions, with random overlap
parameters. Example shown in Figure \ref{fig:simulation_examples} and details in
\ref{apd:experiments:generation}.

@@

    \caption{Example of the simulation setup in the input space with two
        knots --\emph{ie.}basis functions. The top panel
        shows the observations in feature space, while the bottom panel displays the
        two response surfaces on a 1D cut along the black lines drawn on
        the top panel.}
    \label{fig:simulation_examples}
\end{figure}

@@

We use Gaussian-distributed covariates and random basis expansion based on
Radial Basis Function kernels. A random basis of RBF kernel enables modeling
non-linear and complex relationships between covariates in a similar way to the
well known spline expansion. The estimators of the response function are learned
with a linear model on another random basis (which can be seen as a stochastic
approximation of the full data kernel \cite{rahimi_random_2008}). We
carefully control the amount of overlap between treated and control populations,
a crucial assumption for causal inference.

@@

>>>>

The $R \text{-risk}$ targets the oracle at the cost of an overlap re-weighting
and the addition of the reweighted Bayes residuals, which are independent of
$f$. In good overlap regions the weights $e(x) \big(1-e(x) \big)$ are close to
$\frac{1}{4}$, hence the $R \text{-risk}$ is close to the desired gold-standard
$\tau \text{-risk}$. For randomized control trials, this weight is constant
making the $R\text{-risk}$ particularly suited for exploring
heterogeneity (Appendix \ref{apd:theory:special_cases})

@@

We generate the response functions using random bases extension, a common method
in biostatistics, \emph{eg} functional regression with splines
\cite{howe_splines_2011, perperoglou_review_2019}. By allowing the function to
vary at specific knots, we control the complexity of the non-linear outcome
models. We use random approximation of Radial Basis Function (RBF) kernels
\cite{rahimi_random_2008} to generate the outcome and treatment functions. RBF
use the same process as polynomial splines but replace polynomial by Gaussian
kernels. Unlike polynomial, Gaussian kernels have decreasing influences in the
input space. This avoids unrealistic divergences of the response surfaces at the
ends of the feature space. We generate 1\,000 datasets based on these functions,
with random overlap parameters. Example shown in Figure
\ref{fig:simulation_examples} and details in \ref{apd:experiments:generation}.

@@

@@

We use Gaussian-distributed covariates and random basis expansion based on
Radial Basis Function kernels. A random basis of RBF kernel enables modeling
non-linear and complex relationships between covariates in a similar way to the
well known spline expansion. The estimators of the response function are learned
with a linear model on another random basis (which can be seen as a stochastic
approximation of the full data kernel \cite{rahimi_random_2008}). We carefully
control the amount of overlap between treated and control populations, a crucial
assumption for causal inference. Figure \ref{fig:simulation_examples}
illustrates 2D examples of the simulation.

@@

    \caption{Example of the simulation setup in the input space with two
        knots --\emph{ie.} basis functions. The top panel
        shows the observations in feature space, while the bottom panel displays the
        two response surfaces on a 1D cut along the black lines drawn on
        the top panel.}
    \label{fig:simulation_examples}
\end{figure}
